getdata3.Rmd

### 2021-12-19 getdata3.Rmd
continuing ..

```{r fromobs}
bobs <- obs[obs$starttyp == 2 & obs$id %in% per$id, ]

```

>>>>

```{r fromobs}
bobs <- obs[obs$starttyp == 2 & obs$id %in% per$id, ]
indx <- match(per$id, bobs$id)
per$nofrs <- bobs$nofrs[indx]
per <- per[!is.na(per$nofrs), ]
per$subreg <- factor(per$nofrs)
levels(per$subreg) <- c(rep("ume", 2), 
                        rep("bjur", 4), 
                        rep("sten", 3))
per <- per[(per$subreg != "sten") & per$df == 0, ]
per$subreg <- factor(per$subreg)
```
